---
title: "case_study"
author: "Xinyi Lin"
date: "10/9/2018"
output: html_document
---

```{r}
library(tidyverse)
library(ggridges)
```

```{r}
library(p8105.datasets)
data(nyc_airbnb)

nyc_airbnb
```

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group)
```

```{r}
nyc_airbnb %>% 
  count(boro)

nyc_airbnb %>% 
  count(boro, neighbourhood)
```

## Question:

* Does rating vary by neighborhood, room type or both ?
* How is price related to other variables ?
* What are rentals located ?

* What's the most expensive area ? What about the least ?
* Which listings have the most unfilled days ?
* Which area has the highest density of listings ?
* What are some host characteristics ? How many listings ? What's associated with ratings ?

## Answer

Question 1

```{r}
nyc_airbnb %>% 
  group_by(boro, neighbourhood) %>% 
  summarise(median_star = median(stars), na.rm = TRUE) %>% 
  spread(key = neighbourhood, value = median_star, )
```


```{r}
nyc_airbnb %>% 
  group_by(boro, neighbourhood) %>% 
  summarise(mean_price = mean(price, na.rm = TRUE))
```

Question 3

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point() +
  viridis::scale_color_viridis(discrete = TRUE)
```

choropleth can be draw through ggplot2