---
title: "visualization_1"
author: "Xinyi Lin"
date: "9/27/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```


```{r}
library(tidyverse)
library(ggridges)       #????????what is this package for
```

Here is a illustration of rnoaa
```{r}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

## Start a plot

First scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  )
```

Tick marks and labels

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +
  scale_x_continuous(                 # control x, continuous represent the x type 
    breaks = c(-15, 0, 15),
    labels = c("-15 ºC", "0", "15"),
    limits = c(-20, 42)
  ) +
  scale_y_continuous(
    position = "right",
    trans = "sqrt"           # output sqrt(y)
  )
```

## Color and themes

Adjust color

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +
  scale_color_hue(
    name = "Location",       # give the color a label
    h = c(100, 350),
    l = 75
  )    # seems to be the most powerful scale_color if you want to choose your own color, but usually it is not good to use the color you choose
```

Viridis

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  theme(legend.position = "bottom")    # put the color annotation at bottom
```

## Themes

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  theme_bw()  
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  theme_classic()  
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  ggthemes::theme_excel()
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  theme(legend.position = "bottom") +
  theme_bw()  # this will reset all theme related staff, so in this order, the legend will not in the bottom, we should first "theme_bw~" then "theme(~"
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


Learning Assessment: Revisit the plot showing tmax against date for each location. Use labels, scale options, and theme changes to improve the readability of this plot.

```{r}
ggplot(weather_df, aes(x = date, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) + 
  labs(
    title = "Temperature vs date",
    x = "Date",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
  theme(legend.position = "bottom")
```

## Argument to `geom_*`

```{r}
centralpark_df = 
  weather_df %>% 
  filter(name == "CentralPark_NY")

waikiki_df = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(waikiki_df, aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_line(data = centralpark_df)
```

```{r}
centralpark_df = 
  weather_df %>% 
  filter(name == "CentralPark_NY")

waikiki_df = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(waikiki_df, aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_point(data = centralpark_df)
```

## patchwork

patchwork help us to combind different plots

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = names)) + 
  geom_point(aes(color = name), alpha = .5) + 
    facet_grid(~ name) +
  labs(
    title = "Temperature vs date",
    x = "Date",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) + 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  ) +
    theme_bw() +
    theme(legend.position = "bottom")
```


```{r}
library(patchwork)

tmax_tmin_p = ggplot(weather_df, aes(x = tmax, y = tmin, color = name)) + 
  geom_point(alpha = .5) +
  theme(legend.position = "none")

prcp_dens_p = weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name)) + 
  geom_density(alpha = .5) + 
  theme(legend.position = "none")

tmax_date_p = ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  theme(legend.position = "bottom")

tmax_tmin_p + tmax_date_p
```

```{r}
(tmax_tmin_p + tmax_date_p) / tmax_date_p
```

## Data manipulation

factors ...

```{r}
ggplot(weather_df, aes(x = name, y = tmax, fill = name)) +
  geom_violin(alpha = .5)
```

```{r}
weather_df %>%
  mutate(name = forcats::fct_relevel(name, c("Waikiki_HA", "CentralPark_NY", "Waterhole_WA"))) %>%   # change the order of name
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```

```{r}
weather_df %>%
  mutate(name = forcats::fct_reorder(name, tmax)) %>%   # change the order of name based on the tmax
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```

```{r}
weather_df %>%            # ?????? is there any other possible ways like add two density plots? seems no as the x need to mention in ggplot function, which forbid two x.
  select(name, tmax, tmin) %>% 
  gather(key = observation, value = temp, tmax:tmin) %>% 
  ggplot(aes(x = temp, fill = observation)) +
  geom_density(alpha = .5) + 
  facet_grid(~name) + 
  viridis::scale_fill_viridis(discrete = TRUE)
```



